\RequirePackage{nag}
\documentclass[12pt,letterpaper]{article}
\usepackage{lipsum}

\input{config.tex}

\title{\ruleline{Biographical Sketch}}
\lhead{Zhian N. Kamvar, Ph. D.}
\rhead{Biographical Sketch}
% The Biographical sketch must include the following information:

% * be no more than 2 pages in length, excluding lists of publications;
% * include a presentation of academic, extension, and/or research credentials
%   including, as applicable: earned degrees, teaching experience, employment
%   history, professional activities, honors and awards, and grants received;
% * indicate TOTAL number of undergraduate students directly mentored or trained
%   through experiential learning activities during the past four (4) years; and
% * include all relevant publications in refereed journals during the past four
%   (4) years, including those in submission.
% In addition to the information on Attach Biographical Sketch Field (see Part
% IV, C, 4 c), applicants must include the date of completion of their terminal
% degree. The Biographical sketch of the Primary mentor (more than one Primary
% Mentor if integrated project only) should include the number of mentees
% mentored at least for the last 5 years.

\begin{document}

\maketitle

\begin{center}
{\bf Zhian Namir Kamvar}\\
Department of Plant Pathology \\
University of Nebraska, Lincoln NE 68583\\
Phone: 541-286-0187; Email: \href{mailto:zkamvar@unl.edu}{zkamvar@unl.edu}
\end{center}

\subsection*{Education and Training}  

\begin{center}
\begin{tabular}{lllr}%{p{0.25\linewidth}p{0.3\linewidth}p{0.15\linewidth}p{0.2\linewidth}}
\textbf{Institution} & \textbf{Area} & \textbf{Degree} & \textbf{Awarded}\\
Oregon State University & Botany and Plant Pathology & \textit{\textbf{Ph. D.}} & 2016-12-06\\
Truman State University & Biology  & \textit{\textbf{B. Sc.}} &  2007-12-17
\end{tabular}
\end{center}



\subsection*{Research and Professional Experience}

\begin{tabular}{p{0.15\linewidth}p{0.775\linewidth}}
2017 --	Present & Postdoctoral Research Assistant, Department of Plant Pathology 
			      University of Nebraska (UNL), Lincoln, NE\\
2011 -- 2016    & Graduate Research Assistant, Department of Botany and Plant 
                  Pathology, Oregon State University (OSU), Corvallis, OR
\end{tabular}

\subsection*{Personal Statement}

% My Ph.D. work focused on developing computational tools for the analysis of clonal population genetic data, emphasizing the need for reproducibility in genetic data analysis. 
% I have carried this theme into my postdoctoral research, focusing on local adaptation to thermal regions in the pathogenic fungus, \textit{Sclerotinia sclerotiorum}.
% My career goals are enter into a tenure-track program with both research and education responsibilities.
% Regarding education, I am especially interested in teaching the concepts of reproducible research and science communication to graduate and undergraduate students.
% These two concepts will build the skills necessary for working in 21st century science.

I am a first year postdoctoral scholar working in the intersection of plant pathology, fungal evolutionary biology, and data science. My Ph. D. dissertation focused on developing open source tools for reproducible analysis of clonal pathogen populations. 
\textbf{My ultimate research goal is to understand how clonal plant pathogen populations evolve in agricultural ecosystems.}
As environmental pressures mount from management practices and changing climate, our food security depends on our knowledge of pathogen evolution.
I am also dedicated to the practice of open and reproducible research as there are many well-documented benefits including the potential for making agricultural science a more diverse and inclusive field.

Ideally, I would like to pursue this goal by obtaining a faculty position with
research and teaching responsibilities. 
This would place me in a situation where I would be able to contribute to plant pathology by both mentoring the future generation of scientists and pursuing my research interests on the evolution of clonal plant pathogens.
The teacher training that I would receive through this fellowship would both aid in my acquisition of a faculty position and provide a course that I can take
with me in a new position.

\subsection*{Synergistic Activities}

\subsubsection*{Professional Service}
\begin{enumerate}
	
	\item \textit{\textbf{Ad-hoc peer review for:}} Molecular Ecology, Methods in Ecology and Evolution
	\item \textit{\textbf{Maintainer of:}} NESCent Population Genetics in R  website: 
                                 \href{http://popgen.nescent.org}{popgen.nescent.org}
\end{enumerate}

\subsubsection*{Outreach}

\begin{tabular}{p{0.15\linewidth}p{0.775\linewidth}}
2012 -- 2016 & Co-creator and Host, \textit{Inspiration Dissemination} --- 
			   award-winning science communication radio program interviewing 
			   graduate students about their lives and research at Oregon State 
			   University.\\
2011 -- 2015 & Volunteer at \textit{OSU Discovery Days} --- teaching K-8 students
               about the diversity of plants and fungi.
\end{tabular}

\subsubsection*{Teaching Experience}

\begin{tabular}{p{0.15\linewidth}p{0.775\linewidth}}
Summer 2017  & Introduction to R workshop, University of Nebraska-Lincoln and 
			   North-Central American Phytopathological Society Meeting,
			   Champaign, IL\\
Summer 2016  & Reproducible Research in R Workshop, American Phytopathological 
			   Society (APS) Annual Meeting, Tampa, FL\\
Spring 2016  & Botany 101: A Human Concern, Graduate Teaching Assistant, OSU\\
Summer 2015  & Population Genetics in R Workshop, APS Annual Meeting, Pasadena, CA\\
Summer 2014  & Population Genetics in R Workshop, APS Annual Meeting, Minneapolis, MN\\
Spring 2014  & Population Genetics in R Workshop, OSU\\
Winter 2012  & Biology 212: Intro to Biology, Graduate Teaching Assistant, OSU\\
2008 -- 2011 & English Instructor, Daegu, South Korea\\
Fall 2007    & Cell Biology, Undergraduate Teaching Assistant, TSU\\
Fall 2006    & Cell Biology, Undergraduate Teaching Assistant, TSU
\end{tabular}


\subsection*{Awards and Honors}

\begin{tabular}{p{0.125\linewidth}p{0.8\linewidth}}

2016 & Botany and Plant Pathology Grad. Student Assoc. Travel Award\\
2016 & APS Foundation Student Travel Award\\
2015 & APS Pacific Division Travel Award\\
2015 & OSU Graduate School Travel Award\\
2015 & National Evolutionary Synthesis Center (NESCent) Travel Award for Population Genetics in R Hackathon\\
2014 & OSU Botany and Plant Pathology Anita Summers Travel Award\\
2014 & Most Innovative [Radio] Program (\textit{Intercollegiate Broadcasting System})\\
2013 & Seattle Institute For Statistical Genetics Travel Award\\
2006 & Truman State University Summer Research Stipend\\
2003 & Truman State University Presidential Leadership Scholarship

\end{tabular}

\newpage

\subsubsection*{Peer-Reviewed Publications (last four years)}

\begin{enumerate}[leftmargin = 14pt]

	\item Gr\"unwald NJ, Everhart SE, Knaus BJ, \textbf{Kamvar ZN}. (2017)
	Best practices for population genetic analyses. \textit{Phytopathology}
	\textbf{In Press} doi: \href{http://dx.doi.org/10.1094/PHYTO-12-16-0425-RVW}{10.1094/PHYTO-12-16-0425-RVW}

	\vspace{6pt}

	\item Tabima JF, Everhart SE, Larsen MM, Weisberg AJ, \textbf{Kamvar ZN}, Tancos MA,
	Smart CD, Chang JH, Gr\"unwald NJ. (2016) Microbe-ID: an open source toolbox
	for microbial genotyping and species identification. \textit{PeerJ} \textbf{4}: e2279
	doi: \href{https://doi.org/10.7717/peerj.2279}{10.7717/peerj.2279}
	
	\vspace{6pt}
	
	\item Jombart T, Archer F, Schliep K, \textbf{Kamvar ZN}, Harris R, Paradis
	E, Goudet J, Lapp H (2016). apex: phylogenetics with multiple genes.
	\textit{Molecular Ecology Resources}. \textbf{17}:1 19-26 doi:
	\href{http://dx.doi.org/10.1111/1755-0998.12567}{10.1111/1755-0998.12567}
	
	\vspace{6pt}

	\item \textbf{Kamvar ZN}, L\'opez-Uribe MM, Coughlan S, Gr\"unwald NJ, Lapp
	H, Manel S (2016). Developing educational resources for population genetics
	in R: an open and collaborative approach. \textit{Molecular Ecology Resources}. 
	\textbf{17}:1 120-128 doi:
	\href{http://dx.doi.org/10.1111/1755-0998.12558}{10.1111/1755-0998.12558}
	
	\vspace{6pt}

	\item Gr\"unwald NJ, Larsen MM, \textbf{Kamvar ZN}, Reeser PW, Kanaskie A,
	Laine J, Wiese R (2015) First report of the EU1 clonal lineage of
	\textit{Phytophthora ramorum} on tanoak in an OR forest. 
	\textit{Plant Disease}. \textbf{100}:5, 1024-1024. doi:
	\href{http://dx.doi.org/10.1094/PDIS-10-15-1169-PDN}{10.1094/PDIS-10-15-1169-PDN}
	
	\vspace{6pt}

	\item \textbf{Kamvar ZN}, Brooks JC and Gr\"unwald NJ (2015) Novel R tools for
	analysis of genome-wide population genetic data with emphasis on clonality.
	\textit{Front. Genet.} \textbf{6}: 208. doi: \\
	\href{http://dx.doi.org/10.3389/fgene.2015.00208}{10.3389/fgene.2015.00208}
	
	\vspace{6pt}

	\item \textbf{Kamvar ZN}, Larsen MM, Kanaskie AM, Hansen EM, and Gr\"unwald
	NJ. (2015) Spatial and temporal analysis of populations of the sudden oak
	death pathogen in Oregon forests. \textit{Phytopathology}. \textbf{105}:7
	982-989. doi: 
	\href{http://dx.doi.org/10.1094/PHYTO-12-14-0350-FI}{10.1094/PHYTO-12-14-0350-FI}.
	
	\vspace{6pt}

	\item Weiland JE, Garrido PA, \textbf{Kamvar ZN}, Marek SM, Gr\"unwald NJ, and
	Garz\'on CD. (2015) Population structure of \textit{Pythium irregulare}, \textit{P.
	sylvaticum}, and \textit{P. ultimum} in forest nursery soils of Oregon and
	Washington. \textit{Phytopathology}. \textbf{105}:5 684-694. doi: \\
	\href{http://dx.doi.org/10.1094/PHYTO-05-14-0147-R}{10.1094/PHYTO-05-14-0147-R}
	
	\vspace{6pt}

    \item \textbf{Kamvar ZN}, Tabima JF, Gr\"unwald NJ. (2014) \textit{Poppr}: an
	R package for genetic analysis of populations with clonal, partially clonal,
	and/or sexual reproduction. PeerJ \textbf{2}: e281. doi: \\
	\href{http://dx.doi.org/10.7717/peerj.281}{10.7717/peerj.281}

\end{enumerate}

\end{document}
