\RequirePackage{nag}
\documentclass[12pt,letterpaper]{article}
\input{config.tex}

\title{\ruleline{Budget Justification}}
\lhead{Zhian N. Kamvar, Ph. D.}
\rhead{Budget Justification}

\begin{document}
\maketitle

All cumulative budget categories, with the exception of Indirect Costs, for
which support is requested must be individually listed (with costs) in the same
order as the cumulative budget. NOTE: For continuation awards, all budget
categories for year one must also be fully justified. If consulting,
collaborative, or subcontractual arrangements are included in the application,
these arrangements should be fully explained and justified. The rate of pay for
any consultant must be included, if known at the time of application. Please
include a cost breakdown for the consultant, including the number of days in
service, travel, and per diem, as well as the rate of pay. Letters of consent or
collaboration and other evidence should be provided in the Documentation of
Collaboration (see Part IV, C. 3. f. 5) to show that collaborators have agreed
to participate. A proposed statement of work, biographical sketch, and a budget
for each arrangement involving the transfer of substantive programmatic work or
the provision of financial assistance to a third party must be supplied. In
multi-institutional applications, a budget and budget narrative must be included
for each institution involved. The lead institution and each participating
institution must be identified.

\subsubsection{For Integrated Project Applications} 

Each function should be represented by one or more objectives within the
application. Projects must budget sufficient resources to carry out the proposed
set of research, education, and/or extension activities that will lead to the
desired outcomes. No more than two-thirds of a project's budget may be focused
on a single component.


\subsection{Salary}

A sum of \$99,267 is requested to support an annual salary of \$48,000 with an estimated cost-of-living increase of 3\% for two years.

\subsection{Benefits}

A sum of \$39,707 is requested to support a 40\% rate for benefits.

\subsection{Travel}

A sum of \$4,312 is requested to cover expenses associated with lodging and travel to Washington D.C. for one NIFA AFRI ELI PD meeting and one meeting in the Plant Health and Production and Plant Products Foundational Program Area.

\$4,000 is requested for travel, tuition, and room and board for the Workshop on Molecular Evolution in Woods Hole, MA.

\$2,000 is requested for travel to the Northstar Summer Institute for Scientific Teaching in Twin Cities, MI.

\end{document}
