\RequirePackage{nag}
\documentclass[12pt,letterpaper]{article}
\usepackage{lipsum}
\input{config.tex}

\title{\ruleline{Key Personnel}}
\lhead{Zhian N. Kamvar, Ph. D.}
\rhead{Key Personnel}


\begin{document}
\maketitle

\begin{quote}
Clearly describe the roles and responsibilities of the PD, collaborator(s), mentor(s), etc.
(biographical sketches should \textbf{not} be included here).
\end{quote}

\subsubsection{Project Director (PD): Zhian N. Kamvar, Ph. D.}

\noindent Dr. Kamvar will serve as PD for the proposed project. 
The fellow is responsible for all aspects of project management, including training/career development project, mentoring, and evaluation plans. 
The fellow is responsible for submitting monthly reports to mentors and an annual summary evaluation report to NIFA.
The fellow is additionally responsible for attending the annual investigators meeting and the Foundational Priority for Plant Health and Production and Plant Products meeting in Washington, DC.
The estimated percent time devoted to educational activities will be 60\% with the remaining 40\% will be dedicated to research activities. 

\subsubsection{Primary Mentor (PM): Sydney E. Everhart, Ph. D.}

\noindent Dr. Everhart will serve as PM for the proposed project. 
The PM will be responsible for providing resources, guidance, and expertise as outlined in the proposal along with lab space, reagents, materials, and monetary items necessary for the sequencing of 96 isolates of \textit{Sclerotinia sclerotiorum}. 
In addition, the PM will be responsible for reviewing and providing critical feedback for monthly project updates from the PD as part of the assessment plan. 

\subsubsection{Collaborative Mentor (CM): Jenny Dauer, Ph. D.}
The CM will be responsible for providing guidance in all matters relating to course development (Objective \#1) and execution (Objective \#4). 
In addition, the CM will be responsible for reviewing monthly project updates from the PD as part of the assessment plan.

\subsubsection{Collaborator: Weidong Chen, Ph. D.}
The collaborator will be responsible for providing isolates of \textit{S. sclerotiorum} from China, collected by his lab and his collaborators, enabling the PD to complete Objectives \#2 and \#3.



\end{document}
